How to Write Theses\\ With Two Line Titles

### 2020-04-15 chapters/results/results.tex
New

In this section we will discuss our findings after implementing the machine learning algorithms and the metamorphic properties.

Accuracy is defined as the number of correct predictions made by the model with respect to the total number of predictions made. To evaluate the accuracy of our machine learning models, we first trained the models on the training data. The MNIST, Fashion-MNIST, and, EMNIST training datasets have 55000, 55000, and, 119800 training data respectively. The training data consists of the images and their corresponding labels which are used as input to the algorithm in order to generate a model. Once we generated the trained models, we used the test data to calculate the accuracy of the models. The MNIST, Fashion-MNIST, and, EMNIST testing dataset have 10000, 10000, and, 20800 testing data respectively. The following graphs show the accuracy of the various models on the test dataset.

\pgfplotstableread[row sep=\\,col sep=&]{
    interval & MNIST & Fashion & EMNIST \\
    CNN     & 97.01 & 83.56 & 78.20 \\
    NN     & 91.41 & 79.89 & 64.96 \\
    NB    & 80.85 & 65.6 & 57.81 \\
    KNN   & 97.28 & 85.24 & 86.25 \\
    SVM   & 95.47 & 84.56 & 81.25\\
    }\accuracy

\begin{center}
\begin{tikzpicture}
    \begin{axis}[
            ybar,
            bar width=.75cm,
            height=.5\textwidth,
            width=\textwidth,
            legend style={at={(0.5,1)},
                anchor=north,legend columns=-1},
            symbolic x coords={CNN,NN,NB,KNN, SVM},
            xtick=data,
            ytick={0,20,40,60,80,100},
            nodes near coords,
            nodes near coords align={vertical},
            ymin=0,ymax=120,
            ylabel={Accuracy},
            xlabel={Algorithms}
        ]
        \addplot table[x=interval,y=MNIST]{\accuracy};
        \addplot table[x=interval,y=Fashion]{\accuracy};
        \addplot table[x=interval,y=EMNIST]{\accuracy};
        \legend{MNIST, Fashion, EMNIST}
    \end{axis}
\end{tikzpicture}      
\end{center}{}
An interesting observation from the table above is that, deep learning algorithms are not necessarily always a good choice when we are trying to maximize accuracy. Depending on the type of dataset, regular machine learning algorithms like KNN can also yield high accuracy and outperform deep learning algorithms.
In the following sections we will discuss how the metamorphic transformations affected the accuracy of the models and what conclusions we can draw from it.
\section{Effect of metamorphic transformation on the accuracy of the model}
From literature review we saw that metamorphic testing can be a very useful technique to test the correctness of an algorithm. In this thesis, we will investigate the effect of the identified metamorphic properties on the accuracy of the machine learning algorithms. For each metamorphic property identified in \ref{identifyingMR} we want to see how the accuracy of the models change with the varying degree of transformation. Our hypothesis is that small changes to the input image should not affect the prediction of the model drastically. After creating a trained model with the training dataset, we applied the metamorphic properties on the training data to generate transformed versions of the test data. We calculated the following metrics to evaluate the effect of the metamorphic relations on machine learning algorithm. To tackle the stochastic nature of training a neural network model, we ran each of the above experiment ten times and calculated average for accuracy.

\input{figures.tex}

@@

\newpage
\section{Discussion}
In this paper we identified five metamorphic properties "Rotation", "Shading", "Shearing", "Shifting the image along $x$ axis", and, "Shifting the image along $y$ axis" that can be used with image datasets. We then applied these metamorphic transformations to three datasets: MNIST, Fashion-MNIST, and, EMNIST. We also looked at how the accuracy of the datasets are affected by the transformations we identified. We also investigated the accuracy of transformations on individual classes in the MNIST dataset. We then provide recommendations for creating follow up test cases from the MNIST dataset by using the minimum and maximum values of transformations to use for these metamorphic properties. We also implemented five common machine learning algorithms and evaluated their robustness on these metamorphic properties.
We make following recommendations for transforming digits in MNIST dataset.
This paper also make the following contributions: 
We made a methodological contribution where we have provided a set of functions to easily manipulate, and, transform image datasets for future research. Future researchers can utilize these functions to plugin more algorithms and metamorphic properties.

Contributions:
Methodological contribution where others can plugin more algors or MT.
Experimental contribution:Which algo does better.

Conclusions:

Framework to apply MT in midst of distortions.
CNN not so much better than others based on learning just from the dataset.

>>>>

In this section, we will discuss our findings after implementing the machine learning algorithms and metamorphic properties.

Accuracy is defined as the number of correct predictions made by the model with respect to the total number of predictions made. To evaluate the accuracy of our machine learning models, we first trained the models on the training data. The MNIST, Fashion-MNIST, and EMNIST-Letter training datasets have 55000, 55000, and 119800 training data, respectively. The training data consists of images and their corresponding labels, which are used as input to the algorithm to generate a model. Once we generated the trained models, we used the test data to calculate the accuracy of the models. The following graphs show the accuracy of the various models on the original test dataset.

\pgfplotstableread[row sep=\\,col sep=&]{
    interval & MNIST & Fashion & EMNIST-Letter \\
    CNN     & 97.01 & 83.56 & 78.20 \\
    NN     & 91.41 & 79.89 & 64.96 \\
    NB    & 80.85 & 65.6 & 57.81 \\
    KNN   & 97.28 & 85.24 & 86.25 \\
    SVM   & 95.47 & 84.56 & 81.25\\
    }\accuracy

\begin{center}
\begin{tikzpicture}
    \begin{axis}[
            ybar,
            bar width=.75cm,
            height=.5\textwidth,
            width=\textwidth,
            legend style={at={(0.5,1)},
                anchor=north,legend columns=-1},
            symbolic x coords={CNN,NN,NB,KNN, SVM},
            xtick=data,
            ytick={0,20,40,60,80,100},
            nodes near coords,
            nodes near coords align={vertical},
            ymin=0,ymax=120,
            ylabel={Accuracy},
            xlabel={Algorithms}
        ]
        \addplot table[x=interval,y=MNIST]{\accuracy};
        \addplot table[x=interval,y=Fashion]{\accuracy};
        \addplot table[x=interval,y=EMNIST]{\accuracy};
        \legend{MNIST, Fashion, EMNIST}
    \end{axis}
\end{tikzpicture}      
\end{center}{}
An interesting observation from the table above is that deep learning algorithms are not necessarily always the right choice when we are trying to maximize accuracy. Depending on the dataset, regular machine learning algorithms like KNN can also yield high accuracy and outperform deep learning algorithms in terms of accuracy.
In the following sections, we will discuss how the metamorphic transformations affected the accuracy of the models and what conclusions we can draw from it.
\section{Affect of metamorphic transformation on the accuracy of the models}
From the literature review, we saw that metamorphic testing could be an instrumental technique to test the correctness of a program. In this thesis, we will investigate the effect of the identified metamorphic properties on the accuracy of the machine learning algorithms. For each metamorphic property identified in \ref{identifyingMR}, we want to see how the accuracy of the models changes with the varying degree of transformation. We hypothesize that small changes to the input image should not affect the prediction of the model drastically. After creating a trained model with the training dataset, we applied the metamorphic properties on the training data to generate transformed versions of the test data. We calculated the following metrics to evaluate the effect of metamorphic relations on the machine learning algorithm we implemented. To tackle the stochastic nature of training a neural network model, we ran each of the above experiments ten times and calculated the average accuracy of the models on the transformed datasets.
\input{figures.tex}

@@

\newpage
\section{Discussion}
In this paper we identified five metamorphic properties "Rotation", "Shading", "Shearing", "Shifting the image along $x$ axis", and, "Shifting the image along $y$ axis" that can be used with image datasets. We then applied these metamorphic transformations to three datasets: MNIST, Fashion-MNIST, and, EMNIST. We then implemented five machine learning algorithms and measured the accuracy of the three datasets as well as the accuracy on the transformed dataset. We also investigated the accuracy of transformations on individual classes in the MNIST dataset and provided recommendations for creating follow up test cases from the MNIST dataset. These recommendations include the minimum and maximum values of transformations that can be used for the metamorphic properties. We also evaluated the robustness of the machine learning algorithms on these metamorphic properties. From this evaluation we found that convolutional neural-networks are more robust than the other machine learning algorithms we implemented. \\
This paper also makes the a methodological contribution where we have provided a set of functions on the project's github page to easily manipulate, and, transform image datasets for future research. 
% These functions can be used as frameworks to . 
Future researchers can utilize these functions to plugin more algorithms and metamorphic properties.

% Contributions:
% Methodological contribution where others can plugin more algors or MT.
% Experimental contribution:Which algo does better.

% Conclusions:

% Framework to apply MT in midst of distortions.
% CNN not so much better than others based on learning just from the dataset.
